Motif roles provides unique information about species risk of extinction\\ \medskip Supplementary Information

### 2022-03-01 manuscript/supplement_motifs.tex

    While niche-model food webs can contain cycles (e.g., species A eats B, B eats C, and C eats A), such cycles make it impossible to calculate persistence in the Bayesian network framework~\citep{Tarjan1972}. 
    We therefore removed any cycles within each network by removing the link in each cycle which contributed least to the robustness of the food web, following~\citet{Allesina2009}.
    This is achieved by first finding the set of resources for each consumer and then removing the consumer-resource connections which have the lowest eigenvalue centrality~\citep{Allesina2009functional}.
    These links have the least effect on the overall stability of the network; removing them creates an acyclic network with very similar properties to the original network.
    Next, we ordered the species from lowest to highest trophic level using a topological sorting routine following \citet{Tarjan1972} and \citet{Allesinaetal2005}, ensuring that probability calculations follow a strict bottom-up order. 
    After these steps, calculations of persistence probabilities can begin.

@@

\bibliography{anna_bib} % Abbreviate journal titles.
\bibliographystyle{ecollett}

>>>>

    While niche-model food webs can contain cycles (e.g., species A eats B, B eats C, and C eats A), such cycles make it impossible to calculate persistence in the Bayesian network framework~\citep{Tarjan1972}. 
    We therefore removed any cycles within each network by removing the link in each cycle which contributed least to the robustness of the food web, following~\citet{Allesina2009functional}.
    This is achieved by first finding the set of resources for each consumer and then removing the consumer-resource connections which have the lowest eigenvalue centrality~\citep{Allesina2009functional}.
    These links have the least effect on the overall stability of the network; removing them creates an acyclic network with very similar properties to the original network.
    Next, we ordered the species from lowest to highest trophic level using a topological sorting routine following \citet{Tarjan1972} and \citet{Allesinaetal2005}, ensuring that probability calculations follow a strict bottom-up order. 
    After these steps, calculations of persistence probabilities can begin.

@@

\bibliography{anna_bib_new} % Abbreviate journal titles.
\bibliographystyle{ecollett}
